---
title: "Portfolio 1"
---

> The aim of this first portfolio piece is to document my search process of relevant data for my topic. I have consistent interest in the topic of traumatic brain injuries and mental health issues. I hope to find data that can speak to this topic; however, this portfolio is to introduce my research process and decide on a data set for the rest of my inquires.   

I will begin by loading the tidyverse packages that can assist with further analysis of any data set I find.
```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidyr)

```

I started my search with the "Harvard Dataverse" database. In the search bar I began with the prompt "(traumatic brain injury) AND (mental health)". This search prompt yielded 2,040 results. An initial difficulty I stumbled across is that many of the data sets are restricted due to containing unique patient information. In order to carry on my search I had to filter my results to only include data sets that are set to public, and in doing so limited the results to 420. 

I initially explored a data set that was interesting to me that observes the relationship between childhood trauma and mentalization capacities and dissociative experiences. I was able to successfully open this data set in SPSS and observe the variables measured more closely. This data set consists of 101 participants and 448 variables that would be extremely helpful in observing a variety of inquires. However, I still want to continue my search. 

Next, I examined a different database at "data.gov", and broadened my search to "concussions and mental health". So far, I came across a public data set for "Hospital Encounters for Behavioral Health". I was able to open a .csv file that contains variables such as sex, race, and visit reasons. After looking at this extensive data, I have decided to explore more in depth the summary of data of visits for behavioral health related issues. 

I have downloaded the data set in SPSS, and imported a .sav file in Rstudio for the purposes of examining the data more closely. 

## Download and Import Data

```{r loadpackage}
 library(haven)
 Hospital1 <- read_sav("~/Downloads/hospital-encounters-for-behavioral-health-4ua8pp8u/Hospital1.sav")
glimpse(Hospital1)
```

## Explanation of Variables
In this data there are 9 variables:
```{r variables}
Hospital1["Year"]
```
The variable "Year" includes data for the year the hospital visit occurred, which includes the time frame of 2020-2022

```{r variablegeo}
Hospital1["Geography"]
```

The "Geography" variable expresses where the data came from. 

```{r variabledep}
Hospital1["Pattype"]
```

The variable "Pattype" describes the type of patient seen, either Emergency Department (ED) visit or inpatient.

```{r variablecategory}
Hospital1["Category"]
```
The variable category lays out the foundation for sex, age, race of patient, who paid for the visit, and category of visit such as a special mental health reason or another category.

```{r variablecategorydesc}
Hospital1["Cat_desc"]
```

The variable "Cat_desc" goes off of the previous category variable and specifies the category of the patient e.g., race, sex, age, etc.

```{r variablediagnosis}
Hospital1["Dxgroup"]
```

DX group specifies the reason for the visit for each patient and their specific diagnosis. 

Then, the last 3 variables is count, total, and percentage of individuals per category (e.g., race, sex, Dxgroup, etc).

## Next Steps
In the next portfolio piece I will dive deeper into the breakdown of categories of behavioral health visits and the demographics that make up those categories. 


