---
title: "Portfolio 3"
---

> This project utilizes a dataset that explores engagement ratings of movies and tv shows on Netflix. The data I am focusing on ranges from movies that were released on 2023-2025. Here is the following citation for the dataset available on the repository in TidyTuesday:
Data Science Learning Community (2024). Tidy Tuesday: A weekly social data project. https://tidytues.day



```{r loadpackages}


# Option 2: Read directly from GitHub

movies <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-07-29/movies.csv')
shows <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-07-29/shows.csv')

```

```{r load-packages, message = FALSE}

library(tidyverse) 
devtools::install_github("rstudio-education/dsbox") 
library(dsbox) 

```

My analysis is curated to observe only movies. First, I am curious about the most viewed movies on Netflix that is sorted by hours watched. 

```{r mostviewed}
movies %>% arrange(desc(hours_viewed)) %>% select(title, hours_viewed)

```

Based on sorting movies from most watched in hours, the top 5 movies on Netflix are: Back in Action, Leave the World Behind, Rebel Ridge, and Carry-On.

Next I am curious to see if these top 5 movies are also available globally.

```{r mostglobal}
movies %>% arrange(desc(hours_viewed)) %>% select(title, hours_viewed, available_globally)

```

For the top 5 movies they are all available globally. This makes sense due to more outreach to other countries, these movies have many more opportunities to increase the amount of time people watch them. 

Still going off of movies in descending order, I am curious of the release date for the most watched movies. That is, are the movies with more hours streamed more recent, or just the classics released earlier?

```{r mostviewedgraph}
movies %>% arrange(desc(hours_viewed)) %>% ggplot(aes(x=release_date, y= hours_viewed)) + geom_point() + labs(title = "Most Watched Movies by Date", x= "Release Date", y = "Hours Viewed")

```

According to this graph, the movies that came out recently in 2025 have a very large amount of hours streamed in comparison to earlier years. Based off this graph, it is clear that hours viewed goes up for the more recent movies made. 

Now lets take a look at the same distribution, but with the movies that are available globally. In the following plot I will color in points as red if the movie is not available globally, and I will color the points in green if the movie is available globally. 

```{r graphglobal}
movies %>% arrange(desc(hours_viewed)) %>% ggplot(aes(x=release_date, y= hours_viewed, color = available_globally)) + geom_point() + labs(title = "Most Watched Movies", subtitle = "Distinguished by global availability",x= "Release Date", y = "Hours Viewed") + scale_color_manual(values = c("No" = "red", "Yes" = "green"))

```

Based on this plot, it is still very obvious that the movies that are most watched are also the ones that are available globally. However it is important to note there are a few red dots that depict a few movies in 2025 that are not available globally, yet they are still highly streamed. Let's try to take a look at what movies these exception cases are!

```{r mostglobalextreme}
movies <- movies %>% filter(available_globally == "No") %>% mutate(newmovies = available_globally) 

movies %>% filter(release_date > "2025-01-01") %>%  ggplot(aes(x = release_date, y = hours_viewed)) + geom_point() + facet_grid(~newmovies) + geom_text(aes(label = title), size = 2, vjust = -1, position = "dodge") + labs(title = "Most Watched Movies in 2025", subtitle = "Distinguished by movies that are not globally availabile",x= "Release Date", y = "Hours Viewed")

 
```

Based on this last graph we can see that the most watched movies that are not globally available are "Unexplainable" and "The Heart Knows". 

In all from my findings I have been able to interpret that the most watched movies are those that are both released in 2025 and globally available!



